Simulated Observations of Young Protoplanetary Discs

### 2013-01-22 paper.tex
x

Sensitivities:
C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$
OCS J=$26\rightarrow25$ at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$
HCO$^+$ J=$3\rightarrow2$ at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$
H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$

>>>>

Sensitivities:\newline
C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$
OCS J=$26\rightarrow25$ at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$
HCO$^+$ J=$3\rightarrow2$ at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$
H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$
